---
title: "BSMM-lab-2"
subtitle: "BSMM 8740 Fall 2023"
author: "Zahra Rohaniasl"
date: "9/25/2023"
format: html
editor: visual
self-contained: true
---

## Setup

Load packages and data:

```{r load-pkg-data}
#| message: false
the_tate <- readr::read_delim("data/the-tate-collection.csv", ";", escape_double = FALSE, trim_ws = TRUE)
the_tate_artists <- readr::read_csv("data/the-tate-artists.csv")
```

```{r}
install.packages("tidyverse")
install.packages("tidymodels")
install.packages("gt")
install.packages("gtexplorer")
install.packages("dataexplorer")

```

```{r}
install.packages("VIM")

```

```{r}
library(magrittr)     # the pipe
library(tidyverse)    # for data wrangling + visualization
library(tidymodels)   # for modeling
library(gt)           # for making display tables
library(gtExtras)     # helper functions for beautiful tables
library(DataExplorer)
library(VIM)
library(colorspace)
library(grid)
```

## Exercises

### Exercise 1

The `the_tate` dataset has \_\_\_ unique artists who worked from \_\_\_ to \_\_\_. The works were acquired between the years \_\_\_ and \_\_\_.

```{r}
View(the_tate)
```

```{r}

```

```{r}
library(dplyr)
dplyr::summarize(the_tate, .by = NULL, .groups = NULL)
# Use plot_missing() to visualize missing data
plot_missing(data = the_tate)

DataExplorer::introduce
DataExplorer::plot_missing()

```

```{r}
#unique artists count
unique_artists <- length(unique(the_tate$artist))

# range of years artists worked
#na.omit() is used to remove rows with missing values before calculating the year ranges. 
artists_years <- the_tate %>%
  filter(!is.na(year)) %>%
  summarize(
    start_year = min(year),
    end_year = max(year)
  )

# range of years when works were acquired
acquired_years <- the_tate %>%
  filter(!is.na(acquisitionYear)) %>%
  summarize(
    start_year = min(acquisitionYear),
    end_year = max(acquisitionYear)
  )

# Print the results
cat("The the_tate dataset has", unique_artists, "unique artists who worked from", 
    artists_years$start_year, "to", artists_years$end_year, ".\n")
cat("The works were acquired between the years", acquired_years$start_year, "and", acquired_years$end_year, ".\n")

```

### Exercise 2

How number of works with missing dates is \_\_.

The number of artists whose works have missing dates is \_\_.

It would require resolving missing year data for only \_\_ artists resolve resolve at least 50% of the missing data.

The missing year data likely to be classified as \_\_\_\_.

```{r}
# Count the number of works with missing dates
works_missing_dates <- sum(is.na(the_tate$year))
works_missing_dates

```

```{r}
# Count the number of unique artists with works missing dates
artists_missing_dates <- the_tate %>%
  filter(is.na(year)) %>%
  distinct(Artist) %>%
  n()
artists_missing_dates

```

### Exercise 3

The artist with the most works in the Tate collection is \_\_\_.

The artist with the tenth-most works in the Tate collection is \_\_\_.

### Exercise 4

The artist with the greatest number of works in the Tate collection represent \_\_\_% of the total number of works

### Exercise 5

There are \_\_ duplicate artist-title pairs

### Exercise 6

The artist with the largest work in the tate collection is \_\_\_

The artist with the smallest work in the collection is \_\_\_. The smallest work has area \_\_\_ $\text{cm}^2$

### Exercise 7

...

### Exercise 8

The annual return in the SPX price in 2020 was \_\_\_%.

The corresponding price volatility was \_\_\_%.

### Exercise 9

The period volatility was \_\_\_.\_%

### 
